Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-09 manuscript/manuscript.Rmd
drl

>>>>

## Deep Reinforcement Learning

The policy function $\pi$ often lives in a high- or infinite-dimensional space.
This makes it unfeasible to directly optimize $\pi$.
In practice, an alternative approach is used: $\pi$ is optimized over a much lower-dimensional parametrized family of functions.
Deep reinforcement learning uses this strategy, focusing on function families parametrized by neural networks. (See Fig. \ref{tbd}.)
